Experiment 2 (of 4)

### 2016-07-29 experiments/e2/writeup/e2.Rmd
simplifying the directory by adding function code into the main .Rmd file

```{r print_info_on_design}
# print info on design, number of cells
cat(paste('number of subjects = ',30,'\n',
          '---','\n',
          'number of trials per subject = ',256,'\n', 
          '---','\n',          
          'number of unique cells in the design = Item(4) * Number(2) * Vagueness(2) * Order(2) * Quantity(2) = ',4*2*2*2*2,'\n',
          'number of times a subject saw a unique cell in the design = 256 / 64 = ', 256/64,'\n',
          '---','\n',
          'number of higher-level cells in the design (abstracting over Order and Quantity) = Item(4) * Number(2) * Vagueness(2) = ',4*2*2,'\n',
          'number of times a subject saw a higher level cell in the design =  = 256 / 16 = ', 4*2*2, '\n',
          sep=''))
```

@@

```{r transformations_table, results='asis'}
require(xtable, quietly=TRUE)
x=445
lambda = c(-2,-1,-0.5, 0,0.5,1,2)

xd=data.frame(
  lambda = c(
    lambda[1],
    lambda[2],
    lambda[3],
    lambda[4],
    lambda[5],
    lambda[6],
    lambda[7]
  ),
  x=c(    
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x)
     ),
  conventional=c(
    '$$y=\\frac{1}{x^2}$$', 
    '$$y=\\frac{1}{x}$$', 
    '$$y=\\frac{1}{\\sqrt{x}}$$', 
    '$$y=log_e(x)$$', 
    '$$y=\\sqrt{x}$$', 
    '$$y=x$$', 
    '$$y=x^2$$'
    ),
#   y1=c(    
#     paste("y = ", sep="", 1/(x^2)),
#     paste("y = ", sep="", 1/x),
#     paste("y = ", sep="", 1/sqrt(x)),
#     paste("y = ", sep="", round(log(x),2)),
#     paste("y = ", sep="", sqrt(x)),
#     paste("y = ", sep="", x),
#     paste("y = ", sep="", x^2)
#   ),
  power=c(
    '$$y=x^{-2}$$', 
    '$$y=x^{-1}$$', 
    '$$y=x^{-0.5}$$', 
    '$$y=log_e(x)$$', 
    '$$y=x^{0.5}$$', 
    '$$y=x^{1}$$', 
    '$$y=x^{2}$$'
    ),
  y=c(     
    paste("y = ", sep="", format(round(x^lambda[1],6), sc=F) ),
    paste("y = ", sep="", round(x^lambda[2],3) ),
    paste("y = ", sep="", round(x^lambda[3],3) ),
    paste("y = ", sep="", round(log(x),3) ),
    paste("y = ", sep="", round(x^lambda[5],2) ),
    paste("y = ", sep="", round(x^lambda[6],6) ),
    paste("y = ", sep="", round(x^lambda[7],6) )
  ),
  back = c(
    '$$x=y^{\\frac{1}{-2}}$$',
    '$$x=y^{\\frac{1}{-1}}$$', 
    '$$x=y^{\\frac{1}{-0.5}}$$', 
    '$$x=exp(y)$$',  
    '$$x=y^{\\frac{1}{0.5}}$$', 
    '$$x=y^{\\frac{1}{1}}$$',  
    '$$x=y^{\\frac{1}{2}}$$'
  ),
  back_lambda=c(
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$',
    '$$x=exp(y)$$',  
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$'
  ),
  y_back=c(  
    paste( 'x = ', (x^lambda[1]) ^ {1/lambda[1]} ,sep=""),
    paste( 'x = ', (x^lambda[2]) ^ {1/lambda[2]} ,sep=""),
    paste( 'x = ', (x^lambda[3]) ^ {1/lambda[3]} ,sep=""),
    paste( 'x = ', exp(log(x)), sep=""),
    paste( 'x = ', (x^lambda[5]) ^ {1/lambda[5]} ,sep=""),
    paste( 'x = ', (x^lambda[6]) ^ {1/lambda[6]} ,sep=""),
    paste( 'x = ', (x^lambda[7]) ^ {1/lambda[7]} ,sep="")
  )
)

@@

```{r libs, message=FALSE, results='hide'}
if(require(MASS)){}
if(require(ggplot2)){}
if(require(lmerTest)){}
if(require(xtable)){}
if(require(plyr)){}
if(require(reshape2)){}
if(require(lattice)){}
if(require(LMERConvenienceFunctions)){} # for perSubjectTrim
if(require(car)){}
if(require(rms)){} # for varclus
if(require(gridExtra)){}
if(require(grid)){}
if(require(latticeExtra)){}
if(require(beepr)){}
suppressPackageStartupMessages(require(lme4))
suppressPackageStartupMessages(require(lmerTest))
suppressPackageStartupMessages(require(languageR))
suppressPackageStartupMessages(library("reshape2"))
suppressPackageStartupMessages(library("ggplot2"))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(ggplot2))
if(require(ggplot2)){}
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(plyr))
if(require(reshape2)){}
suppressPackageStartupMessages(require(rms))
suppressPackageStartupMessages(require(languageR))
```

Get the data if file dat.Rda does not already exist.

```{r, get_the_data}
# if the output file dat.Rda already exists then load it, else do data wrangling
if( file.exists('dat.Rda') ) load('dat.Rda') else {

  # source required data wrangling functions
  source('functions/classifyResponse.R')
  source('functions/gatherData.R')

  # declare local variables
  number_of_valid_subjects <- 30
  number_of_rows <- 7680 # 7680
  number_of_trials_per_subject <- number_of_rows / number_of_valid_subjects # 256

    ## call user-defined functions

  # collect all individual subject files into one data frame
  dat <- gatherData(number_of_valid_subjects)

  # classify the response as expected, near, or far
  dat <- classifyResponse(dat)

   ## treat variables

  # SUBJECT
  # ensure Subject is a factor 
  dat$Subject=factor(paste("s",sprintf("%02d",dat$Subject),sep=""))

  # TRIAL
  # Trial for subject, 1 to 256
  dat$Trial = rep(x = 1:number_of_trials_per_subject, times = number_of_valid_subjects)

  # make a centred Trial for modeling
  dat$c_Trl <-dat$Trial - mean(dat$Trial)

  # make a scaled Trial for modelling
  dat$s_Trl <- as.numeric(scale(dat$Trial))

  # ID
  # id is a unique identifier for the 7680 row data
  dat$id <- factor(paste(paste(dat$Subject), 
                         paste("t", sprintf("%03d", dat$Trial), sep="") , sep=":"))

  # ITEM
  # create a centred numeric item variable for modeling
  dat$c_Itm <- ifelse(dat$Item==1, -.75, 
                      ifelse(dat$Item==2, -.25,
                             ifelse(dat$Item==3, .25, .75)))

  # make Item be a factor and assign labels
  dat$Item <- factor(dat$Item, levels=c(1,2,3,4), labels=c("06:15:24", "16:25:34", "26:35:44", "36:45:54"))

  # add ratios for Item
  item_range_ratio = c(6 / 24, 16 / 34, 26 / 44, 36 / 54) 
          # 0.2500000 0.4705882 0.5909091 0.6666667
  item_range_ratio_scaled = as.vector(scale(c(6 / 24, 16 / 34, 26 / 44, 36 / 54)))
          # -1.3441995 -0.1316642  0.5297187  0.9461450
  item_mean_ratio = c(mean(c(6 / 15, 15 / 24)), mean(c(16 / 25, 25 / 34)), mean(c(26 /35, 35 / 44)), mean(c(36 / 45, 45 / 54))) 
          # 0.5125000 0.6876471 0.7691558 0.8166667
  item_mean_ratio_scaled = as.vector(scale(c(mean(c(6 / 15, 15 / 24)), mean(c(16 / 25, 25 / 34)), mean(c(26 /35, 35 / 44)), mean(c(36 / 45, 45 / 54))))) 
          # -1.37582241 -0.06614191  0.54334858 0.89861574

  dat[dat$Item == "06:15:24", "item_range_ratio"] <-  0.2500000
  dat[dat$Item == "16:25:34", "item_range_ratio"] <-  0.4705882
  dat[dat$Item == "26:35:44", "item_range_ratio"] <-  0.5909091
  dat[dat$Item == "36:45:54", "item_range_ratio"] <-  0.6666667

  dat[dat$Item == "06:15:24", "item_range_ratio_scaled"] <-  -1.3441995
  dat[dat$Item == "16:25:34", "item_range_ratio_scaled"] <-  -0.1316642
  dat[dat$Item == "26:35:44", "item_range_ratio_scaled"] <-   0.5297187  
  dat[dat$Item == "36:45:54", "item_range_ratio_scaled"] <-   0.9461450

  dat[dat$Item == "06:15:24", "item_mean_ratio"] <-  0.5125000 
  dat[dat$Item == "16:25:34", "item_mean_ratio"] <-  0.6876471 
  dat[dat$Item == "26:35:44", "item_mean_ratio"] <-  0.7691558
  dat[dat$Item == "36:45:54", "item_mean_ratio"] <-  0.8166667

  dat[dat$Item == "06:15:24", "item_mean_ratio_scaled"] <-   -1.37582241 
  dat[dat$Item == "16:25:34", "item_mean_ratio_scaled"] <-   -0.06614191 
  dat[dat$Item == "26:35:44", "item_mean_ratio_scaled"] <-    0.54334858 
  dat[dat$Item == "36:45:54", "item_mean_ratio_scaled"] <-    0.89861574

  # VAGUENESS
  # Create a factor coding for Vagueness
  dat[ dat$Condition==1 , 'Vagueness'] <- 'Vague'
  dat[ dat$Condition==2 , 'Vagueness'] <- 'Crisp'
  dat[ dat$Condition==3 , 'Vagueness'] <- 'Vague'
  dat[ dat$Condition==4 , 'Vagueness'] <- 'Crisp'
  dat$Vagueness <- as.factor(dat$Vagueness)

  # manually center Vagueness
  dat$c_Vag <- ifelse(dat$Vagueness=='Crisp', -.5, .5)

  # NUMBER
  # Create a factor coding for Number use
  dat[ dat$Condition==1 , 'Number'] <- 'Numeric'
  dat[ dat$Condition==2 , 'Number'] <- 'Numeric'
  dat[ dat$Condition==3 , 'Number'] <- 'Verbal'
  dat[ dat$Condition==4 , 'Number'] <- 'Verbal'
  dat$Number <- as.factor(dat$Number)

  # manually center Number
  dat$c_Num <- ifelse(dat$Number=='Numeric', -.5, .5)

  # CONDITION
  # make a factor out of Condition, as f_Cnd
  dat$f_Cnd <- factor(dat$Condition, levels=c(1,2,3,4), labels=c('Vg:Nm', 'Cr:Nm', 'Vg:Vb', 'Cr:Vb'))

  # ORDER
  # give the levels of Order meaningful names
  dat$Order <- factor(dat$Order, levels=c(1,2), labels=c('LtoR','RtoL'))

  # make a manually centred Order
  dat$c_Ord <- ifelse(dat$Order=="LtoR",-.5,.5)

  # QUANTITY
  # give the levels of Quantity meaningful names
  dat$Quantity <- factor(dat$Quantity, levels=c(1,2), labels=c('Small','Large'))

  # make a manually centred Quantity
  dat$c_Qty <- ifelse(dat$Quantity=="Small",-.5,.5)

  # INSTRUCTION
  # add number of characters in the instruction # 29 30 34 36 38
  dat$nchar_instr = nchar(dat$Instruction)
  dat$nchar_instr_scaled = as.vector(scale(nchar(dat$Instruction), scale=TRUE))

  # make Instruction be a factor (17 levels)
  dat$Instruction <- as.factor(dat$Instruction)

  # RT
  # add transformations of RT
  dat$RT_RecSqd    <- 1/dat$RT^2
  dat$RT_Rec       <- 1/dat$RT
  dat$RT_RecSqt    <- 1/sqrt(dat$RT) 
  dat$RT_log       <- log(dat$RT)
  dat$RT_sqt       <- sqrt(dat$RT)
  dat$RT_raw       <- dat$RT
  dat$RT_sqd       <- dat$RT^2

  # print to file a table with information about the design
  design_info <- unique(subset(dat, select=c(Item, Condition, Vagueness, Number, Quantity, Order, 
                                             Left, Mid, Right, Exp_Num, Bline_Num, Extr_Num, Exp_side, Bline_side, Extr_side,Instruction)))
  design.info <- design_info[order(design_info$Item, design_info$Condition, design_info$Quantity, design_info$Order),]
  row.names(design_info) <- NULL
  capture.output(  print.data.frame(design_info, row.names=F, print.gap=3, quote=F, right=F), file="design_info.table")

  # put dat in better column order
  dat <- subset(dat, 
                select = c(id, Subject, Trial, Condition, Order, Quantity, Vagueness, Number, 
                           Item, item_range_ratio, item_range_ratio_scaled, item_mean_ratio, item_mean_ratio_scaled,
                           c_Trl, s_Trl, c_Itm, c_Vag, c_Num, f_Cnd, c_Ord, c_Qty,
                           RT, RT_RecSqd, RT_Rec, RT_RecSqt, RT_log, RT_sqt, RT_raw, RT_sqd,
                           Exp_Num, Bline_Num, Extr_Num, Exp_side, Bline_side, Extr_side, response_num, response_side, response_category, Left, Mid, Right,
                           Instruction, nchar_instr
                ))

  # save dat as dat.Rda
  # This data set contains *all* trials 7680 including impossible trials and is mainly for graphs comparing different removals
  save(dat, file="dat.Rda")

  ####################################################
  # remove impossible trials from dat in new data dd #
  ####################################################

  # Throw out RT = 1 and RT = 59998, and RTprev = 1 and RTprev = 59998 
  # i.e., throw out sticky fingers and timeouts, 
  # and the trials that followed sticky fingers and timeouts 
  # since they were likely affected by unusual previous trials.

  # lose impossible trials
  dd <- dat
  dd$RT[dd$RT == 1 ] <- NA
  dd$RT[dd$RT == 59998 ] <- NA
  dd <- dd[complete.cases(dd),]
  row.names(dd) <- NULL

>>>>

```{r loadKnitr}
suppressPackageStartupMessages(library(knitr))
```

```{r loadLibs}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(lattice))
suppressPackageStartupMessages(library(latticeExtra))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(beepr))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(LMERConvenienceFunctions)) # for perSubjectTrim
suppressPackageStartupMessages(library(languageR))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(rms))                      # for varclus
suppressPackageStartupMessages(library(languageR))
```

```{r CIfunctions}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  require(plyr)
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  # This is does the summary; it's not easy to understand...
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun= function(xx, col, na.rm) {
                   c( N    = length2(xx[,col], na.rm=na.rm),
                      mean = mean   (xx[,col], na.rm=na.rm),
                      sd   = sd     (xx[,col], na.rm=na.rm)
                   )
                 },
                 measurevar,
                 na.rm
  )
  # Rename the "mean" column    
  datac <- rename(datac, c("mean"=measurevar))
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  return(datac)
}
## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {
  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
                       FUN=is.factor, FUN.VALUE=logical(1))
  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }
  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)
  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL
  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)
  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")
  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)
  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                                  FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )
  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor
  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}
## Norms the data within specified groups in a data frame; it normalizes each
## subject (identified by idvar) so that they have the same mean, within each group
## specified by betweenvars.
##   data: a data frame.
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   na.rm: a boolean that indicates whether to ignore NA's
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
  require(plyr)
  # Measure var on left, idvar + between vars on right of formula.
  data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
                         .fun = function(xx, col, na.rm) {
                           c(subjMean = mean(xx[,col], na.rm=na.rm))
                         },
                         measurevar,
                         na.rm
  )
  # Put the subject means with original data
  data <- merge(data, data.subjMean)
  # Get the normalized data in a new column
  measureNormedVar <- paste(measurevar, "_norm", sep="")
  data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
    mean(data[,measurevar], na.rm=na.rm)
  # Remove this subject mean column
  data$subjMean <- NULL
  return(data)
}

```{r print_info_on_design}
cat(paste('number of subjects = ',30,'\n',
          '---','\n',
          'number of trials per subject = ',256,'\n', 
          '---','\n',          
          'number of unique cells in the design = Item(4) * Number(2) * Vagueness(2) * Order(2) * Quantity(2) = ',4*2*2*2*2,'\n',
          'number of times a subject saw a unique cell in the design = 256 / 64 = ', 256/64,'\n',
          '---','\n',
          'number of higher-level cells in the design (abstracting over Order and Quantity) = Item(4) * Number(2) * Vagueness(2) = ',4*2*2,'\n',
          'number of times a subject saw a higher level cell in the design =  = 256 / 16 = ', 4*2*2, '\n',
          sep=''))
```

@@

```{r transformations_table, results='asis'}
x=445
lambda = c(-2,-1,-0.5, 0,0.5,1,2)

xd=data.frame(
  lambda = c(
    lambda[1],
    lambda[2],
    lambda[3],
    lambda[4],
    lambda[5],
    lambda[6],
    lambda[7]
  ),
  x=c(    
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x),
    paste("x = ", sep="", x)
     ),
  conventional=c(
    '$$y=\\frac{1}{x^2}$$', 
    '$$y=\\frac{1}{x}$$', 
    '$$y=\\frac{1}{\\sqrt{x}}$$', 
    '$$y=log_e(x)$$', 
    '$$y=\\sqrt{x}$$', 
    '$$y=x$$', 
    '$$y=x^2$$'
    ),
  power=c(
    '$$y=x^{-2}$$', 
    '$$y=x^{-1}$$', 
    '$$y=x^{-0.5}$$', 
    '$$y=log_e(x)$$', 
    '$$y=x^{0.5}$$', 
    '$$y=x^{1}$$', 
    '$$y=x^{2}$$'
    ),
  y=c(     
    paste("y = ", sep="", format(round(x^lambda[1],6), sc=F) ),
    paste("y = ", sep="", round(x^lambda[2],3) ),
    paste("y = ", sep="", round(x^lambda[3],3) ),
    paste("y = ", sep="", round(log(x),3) ),
    paste("y = ", sep="", round(x^lambda[5],2) ),
    paste("y = ", sep="", round(x^lambda[6],6) ),
    paste("y = ", sep="", round(x^lambda[7],6) )
  ),
  back = c(
    '$$x=y^{\\frac{1}{-2}}$$',
    '$$x=y^{\\frac{1}{-1}}$$', 
    '$$x=y^{\\frac{1}{-0.5}}$$', 
    '$$x=exp(y)$$',  
    '$$x=y^{\\frac{1}{0.5}}$$', 
    '$$x=y^{\\frac{1}{1}}$$',  
    '$$x=y^{\\frac{1}{2}}$$'
  ),
  back_lambda=c(
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$',
    '$$x=exp(y)$$',  
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$',
    '$$x=y^{1/\\lambda}$$'
  ),
  y_back=c(  
    paste( 'x = ', (x^lambda[1]) ^ {1/lambda[1]} ,sep=""),
    paste( 'x = ', (x^lambda[2]) ^ {1/lambda[2]} ,sep=""),
    paste( 'x = ', (x^lambda[3]) ^ {1/lambda[3]} ,sep=""),
    paste( 'x = ', exp(log(x)), sep=""),
    paste( 'x = ', (x^lambda[5]) ^ {1/lambda[5]} ,sep=""),
    paste( 'x = ', (x^lambda[6]) ^ {1/lambda[6]} ,sep=""),
    paste( 'x = ', (x^lambda[7]) ^ {1/lambda[7]} ,sep="")
  )
)

@@

Load the file dat.Rda if it exists, else Get the data if file dat.Rda does not already exist.

```{r, get_the_data}
# if the output file dat.Rda already exists then load it, else do data wrangling
if( file.exists('dat.Rda') && file.exists('dd.Rda') ) {
	load('dat.Rda'); load('dd.Rda')
	} else {
	gatherData = function(number_of_valid_subjects) {
		data_dir <- '../experimentCode/output/'
		column.headers.df <-  head( read.table(
			paste(data_dir,'subject1.data',sep=''),
			header=TRUE),0)
		gathered.data <- column.headers.df
		for (subject in 1:number_of_valid_subjects) {
			current.filename <- paste(data_dir, 'subject', subject, '.data', sep='')
			current.data <- read.table(file=current.filename, header=TRUE, stringsAsFactors = FALSE)
			gathered.data <- rbind(gathered.data, current.data)
		}
		return(gathered.data)
	} # end of gatherData function
	classifyResponse = function(dat) {
		# what were they expected to respond?
		dat$crossed = as.factor(paste('Con', dat$Condition, ':Quan', dat$Quantity, ':Item', dat$Item, sep=''))
		dat[dat$crossed=='Con1:Quan1:Item1', 'Exp_Num'] <-  6
		dat[dat$crossed=='Con1:Quan1:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con1:Quan1:Item1', 'Extr_Num']      <- 24
		dat[dat$crossed=='Con1:Quan1:Item2', 'Exp_Num'] <- 16
		dat[dat$crossed=='Con1:Quan1:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con1:Quan1:Item2', 'Extr_Num']      <- 34
		dat[dat$crossed=='Con1:Quan1:Item3', 'Exp_Num'] <- 26
		dat[dat$crossed=='Con1:Quan1:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con1:Quan1:Item3', 'Extr_Num']      <- 44
		dat[dat$crossed=='Con1:Quan1:Item4', 'Exp_Num'] <- 36
		dat[dat$crossed=='Con1:Quan1:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con1:Quan1:Item4', 'Extr_Num']      <- 54
		dat[dat$crossed=='Con1:Quan2:Item1', 'Exp_Num'] <- 24
		dat[dat$crossed=='Con1:Quan2:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con1:Quan2:Item1', 'Extr_Num']      <-  6
		dat[dat$crossed=='Con1:Quan2:Item2', 'Exp_Num'] <- 34
		dat[dat$crossed=='Con1:Quan2:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con1:Quan2:Item2', 'Extr_Num']      <- 16
		dat[dat$crossed=='Con1:Quan2:Item3', 'Exp_Num'] <- 44
		dat[dat$crossed=='Con1:Quan2:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con1:Quan2:Item3', 'Extr_Num']      <- 26
		dat[dat$crossed=='Con1:Quan2:Item4', 'Exp_Num'] <- 54
		dat[dat$crossed=='Con1:Quan2:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con1:Quan2:Item4', 'Extr_Num']      <- 36
		dat[dat$crossed=='Con2:Quan1:Item1', 'Exp_Num'] <-  6
		dat[dat$crossed=='Con2:Quan1:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con2:Quan1:Item1', 'Extr_Num']      <- 24
		dat[dat$crossed=='Con2:Quan1:Item2', 'Exp_Num'] <- 16
		dat[dat$crossed=='Con2:Quan1:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con2:Quan1:Item2', 'Extr_Num']      <- 34
		dat[dat$crossed=='Con2:Quan1:Item3', 'Exp_Num'] <- 26
		dat[dat$crossed=='Con2:Quan1:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con2:Quan1:Item3', 'Extr_Num']      <- 44
		dat[dat$crossed=='Con2:Quan1:Item4', 'Exp_Num'] <- 36
		dat[dat$crossed=='Con2:Quan1:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con2:Quan1:Item4', 'Extr_Num']      <- 54
		dat[dat$crossed=='Con2:Quan2:Item1', 'Exp_Num'] <- 24
		dat[dat$crossed=='Con2:Quan2:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con2:Quan2:Item1', 'Extr_Num']      <-  6
		dat[dat$crossed=='Con2:Quan2:Item2', 'Exp_Num'] <- 34
		dat[dat$crossed=='Con2:Quan2:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con2:Quan2:Item2', 'Extr_Num']      <- 16
		dat[dat$crossed=='Con2:Quan2:Item3', 'Exp_Num'] <- 44
		dat[dat$crossed=='Con2:Quan2:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con2:Quan2:Item3', 'Extr_Num']      <- 26
		dat[dat$crossed=='Con2:Quan2:Item4', 'Exp_Num'] <- 54
		dat[dat$crossed=='Con2:Quan2:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con2:Quan2:Item4', 'Extr_Num']      <- 36
		dat[dat$crossed=='Con3:Quan1:Item1', 'Exp_Num'] <-  6
		dat[dat$crossed=='Con3:Quan1:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con3:Quan1:Item1', 'Extr_Num']      <- 24
		dat[dat$crossed=='Con3:Quan1:Item2', 'Exp_Num'] <- 16
		dat[dat$crossed=='Con3:Quan1:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con3:Quan1:Item2', 'Extr_Num']      <- 34
		dat[dat$crossed=='Con3:Quan1:Item3', 'Exp_Num'] <- 26
		dat[dat$crossed=='Con3:Quan1:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con3:Quan1:Item3', 'Extr_Num']      <- 44
		dat[dat$crossed=='Con3:Quan1:Item4', 'Exp_Num'] <- 36
		dat[dat$crossed=='Con3:Quan1:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con3:Quan1:Item4', 'Extr_Num']      <- 54
		dat[dat$crossed=='Con3:Quan2:Item1', 'Exp_Num'] <- 24
		dat[dat$crossed=='Con3:Quan2:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con3:Quan2:Item1', 'Extr_Num']      <-  6
		dat[dat$crossed=='Con3:Quan2:Item2', 'Exp_Num'] <- 34
		dat[dat$crossed=='Con3:Quan2:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con3:Quan2:Item2', 'Extr_Num']      <- 16
		dat[dat$crossed=='Con3:Quan2:Item3', 'Exp_Num'] <- 44
		dat[dat$crossed=='Con3:Quan2:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con3:Quan2:Item3', 'Extr_Num']      <- 26
		dat[dat$crossed=='Con3:Quan2:Item4', 'Exp_Num'] <- 54
		dat[dat$crossed=='Con3:Quan2:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con3:Quan2:Item4', 'Extr_Num']      <- 36
		dat[dat$crossed=='Con4:Quan1:Item1', 'Exp_Num'] <-  6
		dat[dat$crossed=='Con4:Quan1:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con4:Quan1:Item1', 'Extr_Num']      <- 24
		dat[dat$crossed=='Con4:Quan1:Item2', 'Exp_Num'] <- 16
		dat[dat$crossed=='Con4:Quan1:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con4:Quan1:Item2', 'Extr_Num']      <- 34
		dat[dat$crossed=='Con4:Quan1:Item3', 'Exp_Num'] <- 26
		dat[dat$crossed=='Con4:Quan1:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con4:Quan1:Item3', 'Extr_Num']      <- 44
		dat[dat$crossed=='Con4:Quan1:Item4', 'Exp_Num'] <- 36
		dat[dat$crossed=='Con4:Quan1:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con4:Quan1:Item4', 'Extr_Num']      <- 54
		dat[dat$crossed=='Con4:Quan2:Item1', 'Exp_Num'] <- 24
		dat[dat$crossed=='Con4:Quan2:Item1', 'Bline_Num']     <- 15
		dat[dat$crossed=='Con4:Quan2:Item1', 'Extr_Num']      <-  6
		dat[dat$crossed=='Con4:Quan2:Item2', 'Exp_Num'] <- 34
		dat[dat$crossed=='Con4:Quan2:Item2', 'Bline_Num']     <- 25
		dat[dat$crossed=='Con4:Quan2:Item2', 'Extr_Num']      <- 16
		dat[dat$crossed=='Con4:Quan2:Item3', 'Exp_Num'] <- 44
		dat[dat$crossed=='Con4:Quan2:Item3', 'Bline_Num']     <- 35
		dat[dat$crossed=='Con4:Quan2:Item3', 'Extr_Num']      <- 26
		dat[dat$crossed=='Con4:Quan2:Item4', 'Exp_Num'] <- 54
		dat[dat$crossed=='Con4:Quan2:Item4', 'Bline_Num']     <- 45
		dat[dat$crossed=='Con4:Quan2:Item4', 'Extr_Num']      <- 36
		dat$crossed <- NULL
		# what side LEFT, MIDDLE, RIGHT corresponds with Expected, Borderline, Extreme?
		for (row in 1:nrow(dat)) {
			if (dat[row, 'Exp_Num']   == dat[row, 'Left'])  {dat[row, 'Exp_side']   <- 'left'}
			if (dat[row, 'Exp_Num']   == dat[row, 'Mid'])   {dat[row, 'Exp_side']   <- 'mid'}
			if (dat[row, 'Exp_Num']   == dat[row, 'Right']) {dat[row, 'Exp_side']   <- 'right'}
